Financialisation of commodities: co-movement behind-the-scenes

### 2021-09-02 docs/paper.Rmd
github pages

---
title: 'Financialisation of commodities: co-movement behind-the-scenes'
subtitle: "A tale of four factors"
date: "`r format(Sys.Date(), '%B %Y')`"
abstract: |
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that Keynesian and Working’s term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor. Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
bibliography: literature_files/references.bib
output:
  bookdown::gitbook:
    pandoc_args: html.yaml
    split_by: "chapter"
    css: style.css
    toc_depth: 3
    config:
      toc:
        collapse: subsection
        scroll_highlight: true
        before: |
          <li><a href="index.html">Financialization: co-movement</a></li>
      edit: https://github.com/bautheac/financialisation-co-movement/edit/master/docs/%s
      sharing:
        facebook: true
        twitter: true
        whatsapp: true
        all: ['whatsapp', 'twitter', 'facebook']
      download: [ ["paper.pdf", "pdf"] ]
      info: false
    includes:
      after_body: doc_suffix.html
  bookdown::pdf_book:
      pandoc_args: latex.yaml
      base_format: rticles::elsevier_article
      latex_engine: xelatex
      toc_depth: 3
      includes:
        in_header: preamble.tex
---

>>>>

---
title: 'Financialisation of commodities: co-movement behind-the-scenes'
subtitle: A tale of four factors
date: "`r format(Sys.Date(), '%B %Y')`"
bibliography: literature_files/references.bib
github-repo: bautheac/financialisation-co-movement
abstract: |
  The last two decades have seen major changes in the nature of the commodity markets with the influx of financial investor inflows followed by the financial crisis. We study the effects of these events on commodity futures pricing dynamics using commodity asset pricing techniques. We find that Keynesian and Working’s term structure paradigms based factors are best able to detect the effects of commodity financialisation, while the effects of the financial crisis and its aftermath are most clearly visible through the performance of the market factor. Besides, the effects of financialisation seem to go beyond mechanical effects induced by the rise of indexing.
output:
  bookdown::pdf_book:
      pandoc_args: latex.yaml
      base_format: rticles::elsevier_article
      latex_engine: xelatex
      toc_depth: 3
      includes:
        in_header: preamble.tex
  bookdown::gitbook:
    pandoc_args: html.yaml
    split_by: "chapter"
    css: style.css
    toc_depth: 3
    config:
      toc:
        collapse: subsection
        scroll_highlight: true
        before: |
          <li><a href="index.html">Financialization: co-movement</a></li>
        after: |
          <li id="github"><a href="https://github.com/bautheac/financialisation-co-movement"><img src="github.png" alt="github" width="50" height="50"></a></li>
      sharing:
        facebook: true
        twitter: true
        whatsapp: true
        all: ['whatsapp', 'twitter', 'facebook']
      download: [ ["paper.pdf", "pdf"] ]
      info: false
    includes:
      after_body: doc_suffix.html
---

### 2021-09-02 docs/paper.tex
github pages

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465. doi:\href{https://doi.org/10.1016/j.jfineco.2013.03.003}{10.1016/j.jfineco.2013.03.003}

\leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY. doi:\href{https://doi.org/10.2139/ssrn.2348333}{10.2139/ssrn.2348333}

\leavevmode\hypertarget{ref-basak_model_2016}{}%
Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556. doi:\href{https://doi.org/10.1111/jofi.12408}{10.1111/jofi.12408}

@@

\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664. doi:\href{https://doi.org/10.1016/j.jbankfin.2013.02.031}{10.1016/j.jbankfin.2013.02.031}

\leavevmode\hypertarget{ref-bohl_does_2013}{}%
Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616. doi:\href{https://doi.org/10.1017/S1074070800005150}{10.1017/S1074070800005150}

@@

\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694. doi:\href{https://doi.org/10.1002/fut.21756}{10.1002/fut.21756}

@@

\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574. doi:\href{https://doi.org/10.1017/S0022109016000569}{10.1017/S0022109016000569}

\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180. doi:\href{https://doi.org/10.1016/j.finmar.2014.08.001}{10.1016/j.finmar.2014.08.001}

\leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264. doi:\href{https://doi.org/10.1093/ajae/aaw059}{10.1093/ajae/aaw059}

@@

\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70. doi:\href{https://doi.org/10.1016/j.jimonfin.2013.08.004}{10.1016/j.jimonfin.2013.08.004}

\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781. doi:\href{https://doi.org/10.1093/rof/rfu043}{10.1093/rof/rfu043}

\leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441. doi:\href{https://doi.org/10.1146/annurev-financial-110613-034432}{10.1146/annurev-financial-110613-034432}

\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74. doi:\href{https://doi.org/10.1017/S0022109018000765}{10.1017/S0022109018000765}

\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404. doi:\href{https://doi.org/10.1086/258347}{10.1086/258347}

\leavevmode\hypertarget{ref-danthine_information_1978}{}%
Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98. doi:\href{https://doi.org/10.1016/0022-0531(78)90124-2}{10.1016/0022-0531(78)90124-2}

@@

\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182. doi:\href{https://doi.org/10.1086/677836}{10.1086/677836}

\leavevmode\hypertarget{ref-ederington_who_2002}{}%
Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373. doi:\href{https://doi.org/10.1086/338706}{10.1086/338706}

@@

\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521. doi:\href{https://doi.org/10.1093/jjfinec/nbs024}{10.1093/jjfinec/nbs024}

@@

\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297. doi:\href{https://doi.org/10.1002/fut.21656}{10.1002/fut.21656}

\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425. doi:\href{https://doi.org/10.1111/j.1477-9552.2010.00248.x}{10.1111/j.1477-9552.2010.00248.x}

@@

\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322. doi:\href{https://doi.org/10.1111/1477-9552.12068}{10.1111/1477-9552.12068}

\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922. doi:\href{https://doi.org/10.1093/rfs/hht059}{10.1093/rfs/hht059}

\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY. doi:\href{https://doi.org/10.2139/ssrn.2555996}{10.2139/ssrn.2555996}

@@

\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205. doi:\href{https://doi.org/10.1111/iere.12099}{10.1111/iere.12099}

\leavevmode\hypertarget{ref-henderson_new_2015}{}%
Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311. doi:\href{https://doi.org/10.1093/rfs/hhu091}{10.1093/rfs/hhu091}

@@

\leavevmode\hypertarget{ref-hong_what_2012}{}%
Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490. doi:\href{https://doi.org/10.1016/j.jfineco.2012.04.005}{10.1016/j.jfineco.2012.04.005}

@@

\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
Irwin, S.H., 2013. Commodity index investment and food prices: Does the ``masters hypothesis'' explain recent price spikes? Agricultural Economics 44, 29--41. doi:\href{https://doi.org/10.1111/agec.12048}{10.1111/agec.12048}

\leavevmode\hypertarget{ref-irwin_index_2011}{}%
Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31. doi:\href{https://doi.org/10.1093/aepp/ppq032}{10.1093/aepp/ppq032}

\leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396. doi:\href{https://doi.org/10.1017/S1074070800000481}{10.1017/S1074070800000481}

\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391. doi:\href{https://doi.org/10.1017/S1074070800002856}{10.1017/S1074070800002856}

\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649. doi:\href{https://doi.org/10.1002/jae.2388}{10.1002/jae.2388}

\leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27. doi:\href{https://doi.org/10.2307/2967593}{10.2307/2967593}

@@

\leavevmode\hypertarget{ref-kilian_role_2014}{}%
Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478. doi:\href{https://doi.org/10.1002/jae.2322}{10.1002/jae.2322}

\leavevmode\hypertarget{ref-kim_does_2015}{}%
Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714. doi:\href{https://doi.org/10.1002/fut.21716}{10.1002/fut.21716}

\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110. doi:\href{https://doi.org/10.1257/mac.20140033}{10.1257/mac.20140033}

@@

\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY. doi:\href{https://doi.org/10.2139/ssrn.2464400}{10.2139/ssrn.2464400}

\leavevmode\hypertarget{ref-manera_modeling_2016}{}%
Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229. doi:\href{https://doi.org/10.1016/j.eneco.2014.07.001}{10.1016/j.eneco.2014.07.001}

@@

\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250. doi:\href{https://doi.org/10.1016/j.jfineco.2011.11.003}{10.1016/j.jfineco.2011.11.003}

@@

\leavevmode\hypertarget{ref-sanders_new_2011}{}%
Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532. doi:\href{https://doi.org/10.1111/j.1744-7976.2011.01226.x}{10.1111/j.1744-7976.2011.01226.x}

\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94. doi:\href{https://doi.org/10.1093/aepp/ppp006}{10.1093/aepp/ppp006}

@@

\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396. doi:\href{https://doi.org/10.1093/qje/qjt007}{10.1093/qje/qjt007}

\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318. doi:\href{https://doi.org/10.1287/mnsc.2013.1756}{10.1287/mnsc.2013.1756}

\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098. doi:\href{https://doi.org/10.1111/jofi.12261}{10.1111/jofi.12261}

\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60. doi:\href{https://doi.org/10.2139/ssrn.1633908}{10.2139/ssrn.1633908}

@@

\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25. doi:\href{https://doi.org/10.1111/j.1745-6622.1996.tb00295.x}{10.1111/j.1745-6622.1996.tb00295.x}

\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482. doi:\href{https://doi.org/10.1111/jofi.12096}{10.1111/jofi.12096}

\leavevmode\hypertarget{ref-tang_index_2012}{}%
Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74. doi:\href{https://doi.org/10.2469/faj.v68.n6.5}{10.2469/faj.v68.n6.5}

\leavevmode\hypertarget{ref-telser_futures_1958}{}%
Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255. doi:\href{https://doi.org/10.1086/258036}{10.1086/258036}

@@

\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t. Report analysis. Energy Policy 45, 541--550. doi:\href{https://doi.org/10.1016/j.enpol.2012.02.069}{10.1016/j.enpol.2012.02.069}

@@

\leavevmode\hypertarget{ref-working_theory_1948}{}%
Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28. doi:\href{https://doi.org/10.2307/1232678}{10.2307/1232678}

@@

\leavevmode\hypertarget{ref-working_hedging_1953}{}%
Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561. doi:\href{https://doi.org/10.2307/1233368}{10.2307/1233368}

>>>>

\hypertarget{index}{%
\section{Introduction}\label{index}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-acharya_limits_2013}{}%
Acharya, V.V., Lochstoer, L.A., Ramadorai, T., 2013. Limits to arbitrage and hedging: Evidence from commodity markets. Journal of Financial Economics 109, 441--465.

\leavevmode\hypertarget{ref-baker_financialisation_2014}{}%
Baker, S.D., 2014. The financialization of storable commodities (SSRN Scholarly Paper No. ID 2348333). Social Science Research Network, Rochester, NY.

\leavevmode\hypertarget{ref-basak_model_2016}{}%
Basak, S., Pavlova, A., 2016. A model of financialization of commodities. The Journal of Finance 71, 1511--1556.

@@

\leavevmode\hypertarget{ref-basu_capturing_2013}{}%
Basu, D., Miffre, J., 2013. Capturing the risk premium of commodity futures: The role of hedging pressure. Journal of Banking \& Finance 37, 2652--2664.

\leavevmode\hypertarget{ref-bohl_does_2013}{}%
Bohl, M.T., Stephan, P.M., 2013. Does futures speculation destabilize spot prices? New evidence for commodity markets. Journal of Agricultural and Applied Economics 45, 595--616.

@@

\leavevmode\hypertarget{ref-boyd_prevalence_2016}{}%
Boyd, N.E., Büyükşahin, B., Haigh, M.S., Harris, J.H., 2016. The prevalence, sources, and effects of herding. Journal of Futures Markets 36, 671--694.

@@

\leavevmode\hypertarget{ref-brunetti_speculators_2016}{}%
Brunetti, C., Büyükşahin, B., Harris, J.H., 2016. Speculators, prices, and market volatility. Journal of Financial and Quantitative Analysis 51, 1545--1574.

\leavevmode\hypertarget{ref-brunetti_commodity_2014}{}%
Brunetti, C., Reiffen, D., 2014. Commodity index trading and hedging costs. Journal of Financial Markets 21, 153--180.

\leavevmode\hypertarget{ref-bruno_financialisation_2017}{}%
Bruno, V.G., Büyükşahin, B., Robe, M.A., 2017. The financialization of food? American Journal of Agricultural Economics 99, 243--264.

@@

\leavevmode\hypertarget{ref-buyuksahin_speculators_2014}{}%
Büyükşahin, B., Robe, M.A., 2014. Speculators, commodities and cross-market linkages. Journal of International Money and Finance, Understanding international commodity price fluctuations 42, 38--70.

\leavevmode\hypertarget{ref-cheng_convective_2014}{}%
Cheng, I.-H., Kirilenko, A., Xiong, W., 2014. Convective risk flows in commodity futures markets. Review of Finance 19, 1733--1781.

\leavevmode\hypertarget{ref-cheng_financialisation_2014}{}%
Cheng, I.-H., Xiong, W., 2014. Financialization of commodity markets. Annual Review of Financial Economics 6, 419--441.

\leavevmode\hypertarget{ref-christoffersen_factor_2014}{}%
Christoffersen, P., Lunde, A., Olesen, K.V., 2014. Factor structure in commodity futures return and volatility. Journal of Financial and Quantitative Analysis 1--74.

\leavevmode\hypertarget{ref-cootner_returns_1960}{}%
Cootner, P.H., 1960. Returns to speculators: Telser versus keynes. Journal of political Economy 68, 396--404.

\leavevmode\hypertarget{ref-danthine_information_1978}{}%
Danthine, J.-P., 1978. Information, futures prices, and stabilizing speculation. Journal of Economic Theory 17, 79--98.

@@

\leavevmode\hypertarget{ref-duffie_challenges_2014}{}%
Duffie, D., 2014. Challenges to a policy treatment of sSpeculative trading motivated by differences in beliefs. The Journal of Legal Studies 43, S173--S182.

\leavevmode\hypertarget{ref-ederington_who_2002}{}%
Ederington, L., Lee, J.H., 2002. Who trades futures and how: Evidence from the heating oil futures market. The Journal of Business 75, 353--373.

@@

\leavevmode\hypertarget{ref-etula_broker-dealer_2013}{}%
Etula, E., 2013. Broker-dealer risk appetite and commodity returns. Journal of Financial Econometrics 11, 486--521.

@@

\leavevmode\hypertarget{ref-fuertes_commodity_2015}{}%
Fuertes, A.-M., Miffre, J., Fernandez-Perez, A., 2015. Commodity strategies based on momentum, term structure, and idiosyncratic volatility. Journal of Futures Markets 35, 274--297.

\leavevmode\hypertarget{ref-gilbert_how_2010}{}%
Gilbert, C.L., 2010a. How to understand high food prices. Journal of Agricultural Economics 61, 398--425.

@@

\leavevmode\hypertarget{ref-gilbert_role_2014}{}%
Gilbert, C.L., Pfuderer, S., 2014. The role of index trading in price formation in the grains and oilseeds markets. Journal of Agricultural Economics 65, 303--322.

\leavevmode\hypertarget{ref-goldstein_speculation_2014}{}%
Goldstein, I., Li, Y., Yang, L., 2014. Speculation and hedging in segmented markets. The Review of Financial Studies 27, 881--922.

\leavevmode\hypertarget{ref-goldstein_commodity_2017}{}%
Goldstein, I., Yang, L., 2017. Commodity financialization and information transmission (SSRN Scholarly Paper No. ID 2555996). Social Science Research Network, Rochester, NY.

@@

\leavevmode\hypertarget{ref-hamilton_effects_2015}{}%
Hamilton, J.D., Wu, J.C., 2015. Effects of index-fund investing on commodity futures prices. International Economic Review 56, 187--205.

\leavevmode\hypertarget{ref-henderson_new_2015}{}%
Henderson, B.J., Pearson, N.D., Wang, L., 2015. New evidence on the financialization of commodity markets. The Review of Financial Studies 28, 1285--1311.

@@

\leavevmode\hypertarget{ref-hong_what_2012}{}%
Hong, H., Yogo, M., 2012. What does futures market interest tell us about the macroeconomy and asset prices? Journal of Financial Economics 105, 473--490.

@@

\leavevmode\hypertarget{ref-irwin_commodity_2013}{}%
Irwin, S.H., 2013. Commodity index investment and food prices: Does the ``masters hypothesis'' explain recent price spikes? Agricultural Economics 44, 29--41.

\leavevmode\hypertarget{ref-irwin_index_2011}{}%
Irwin, S.H., Sanders, D.R., 2011. Index funds, financialization, and commodity futures markets. Applied Economic Perspectives and Policy 33, 1--31.

\leavevmode\hypertarget{ref-irwin_financialisation_2012}{}%
Irwin, S.H., Sanders, D.R., 2012. Financialization and structural change in commodity futures markets. Journal of Agricultural and Applied Economics 44, 371--396.

\leavevmode\hypertarget{ref-irwin_devil_2009}{}%
Irwin, S.H., Sanders, D.R., Merrin, R.P., 2009. Devil or angel? The role of speculation in the recent commodity price boom (and bust). Journal of Agricultural and Applied Economics 41, 377--391.

\leavevmode\hypertarget{ref-juvenal_speculation_2015}{}%
Juvenal, L., Petrella, I., 2015. Speculation in the oil market. Journal of Applied Econometrics 30, 621--649.

\leavevmode\hypertarget{ref-kaldor_speculation_1939}{}%
Kaldor, N., 1939. Speculation and economic stability. The Review of Economic Studies 7, 1--27.

@@

\leavevmode\hypertarget{ref-kilian_role_2014}{}%
Kilian, L., Murphy, D.P., 2014. The role of inventories and speculative trading in the global market for crude oil. Journal of Applied Econometrics 29, 454--478.

\leavevmode\hypertarget{ref-kim_does_2015}{}%
Kim, A., 2015. Does futures speculation destabilize commodity markets? Journal of Futures Markets 35, 696--714.

\leavevmode\hypertarget{ref-knittel_simple_2016}{}%
Knittel, C.R., Pindyck, R.S., 2016. The simple economics of commodity price speculation. American Economic Journal: Macroeconomics 8, 85--110.

@@

\leavevmode\hypertarget{ref-leclercq_equilibrium_2014}{}%
Leclercq, E., Praz, R., 2014. Equilibrium commodity trading (SSRN Scholarly Paper No. ID 2464400). Social Science Research Network, Rochester, NY.

\leavevmode\hypertarget{ref-manera_modeling_2016}{}%
Manera, M., Nicolini, M., Vignati, I., 2016. Modeling futures price volatility in energy markets: Is there a role for financial speculation? Energy Economics, Energy markets 53, 220--229.

@@

\leavevmode\hypertarget{ref-moskowitz_time_2012}{}%
Moskowitz, T.J., Ooi, Y.H., Pedersen, L.H., 2012. Time series momentum. Journal of Financial Economics, Special issue on investor sentiment 104, 228--250.

@@

\leavevmode\hypertarget{ref-sanders_new_2011}{}%
Sanders, D.R., Irwin, S.H., 2011b. New evidence on the impact of index funds in u.s. Grain futures markets. Canadian Journal of Agricultural Economics/Revue canadienne d'agroeconomie 59, 519--532.

\leavevmode\hypertarget{ref-sanders_adequacy_2010}{}%
Sanders, D.R., Irwin, S.H., Merrin, R.P., 2010. The adequacy of speculation in agricultural futures markets: Too much of a good thing? Applied Economic Perspectives and Policy 32, 77--94.

@@

\leavevmode\hypertarget{ref-simsek_speculation_2013}{}%
Simsek, A., 2013. Speculation and risk sharing with new financial assets. The Quarterly Journal of Economics 128, 1365--1396.

\leavevmode\hypertarget{ref-singleton_investor_2013}{}%
Singleton, K.J., 2013. Investor flows and the 2008 boom/bust in oil prices. Management Science 60, 300--318.

\leavevmode\hypertarget{ref-sockin_informational_2015}{}%
Sockin, M., Xiong, W., 2015. Informational frictions and commodity markets. The Journal of Finance 70, 2063--2098.

\leavevmode\hypertarget{ref-stoll_commodity_2011}{}%
Stoll, H.R., Whaley, R.E., 2011. Commodity index investing: Speculation or diversification? The Journal of Alternative Investments 14, 50--60.

@@

\leavevmode\hypertarget{ref-stulz_rethink_1996}{}%
Stulz, R.M., 1996. Rethinking risk management. Journal of Applied Corporate Finance 9, 8--25.

\leavevmode\hypertarget{ref-szymanowska_anatomy_2014}{}%
Szymanowska, M., De Roon, F., Nijman, T., Van Den Goorbergh, R., 2014. An anatomy of commodity futures risk premia. The Journal of Finance 69, 453--482.

\leavevmode\hypertarget{ref-tang_index_2012}{}%
Tang, K., Xiong, W., 2012. Index investment and the financialization of commodities. Financial Analysts Journal 68, 54--74.

\leavevmode\hypertarget{ref-telser_futures_1958}{}%
Telser, L.G., 1958. Futures trading and the storage of cotton and wheat. Journal of Political Economy 66, 233--255.

@@

\leavevmode\hypertarget{ref-tokic_speculation_2012}{}%
Tokic, D., 2012. Speculation and the 2008 oil bubble: The d.c.o.t. Report analysis. Energy Policy 45, 541--550.

@@

\leavevmode\hypertarget{ref-working_theory_1948}{}%
Working, H., 1948. Theory of the inverse carrying charge in futures markets. Journal of Farm Economics 30, 1--28.

@@

\leavevmode\hypertarget{ref-working_hedging_1953}{}%
Working, H., 1953. Hedging reconsidered. Journal of Farm Economics 35, 544--561.
